---
title: "Lab 01 - Hello R"
author: "Ben Waggener"
date: "01/21/2025"
output: 
  html_document: 
    fig_height: 7
    fig_width: 10
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```

## Exercises

### Exercise 1

The datasaurus_dozen file has 1846 rows and 3 columns (variables?)

### Exercise 2

Here is a plot for the dino data from the datasaurus_dozen dataset

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Here is the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```
The plot depicts a dinosaur and there is a very weak correlation between 'x' and 'y'


### Exercise 3



```{r plot-star}

star_data <- datasaurus_dozen %>%
     filter(dataset == "star")

 ggplot(data = star_data, mapping = aes(x = x, y = y)) +
     geom_point()

```

Plotting the data from the star dataset creates the rough outline of a star

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))

```
There is again a very weak correlation between 'x' and 'y' for this dataset. Similar correlation as the dino dataset.


### Exercise 4


```{r plot-circle}
circle_data <- datasaurus_dozen %>%
     filter(dataset == "circle")

 ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
     geom_point()
 
```

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```

### Exercise 5

Here are all the plots and correlations from the datasaurus_dozen dataset

```{r plot-all}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset)) +
  geom_point() +
  facet_wrap(~dataset, ncol = 3) +
  theme(legend.position = "none")
```

```{r cor-all}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print()
```

